### 2022-07-21 draft.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@a79df87cb25b51991d50fc9341f158dedd48620a 🚀

Our method is in contrast with maximum entropy graph models that predict
a probability distribution on networks under soft or hard constraints
(e.g., Park and Newman 2004; Cimini et al. 2019). We believe our
approach to be more flexible, easier to compute, while allowing direct
comparisons of empirical food webs with more complex networks with
similar structure.

@@

>>>>

@@

\hypertarget{alternative-maxent-models}{%
\subsection{Alternative MaxEnt models}\label{alternative-maxent-models}}

There are different ways to generate food webs using MaxEnt. In this
contribution, we used a method based on simulated annealing to find the
network configuration with the highest SVD entropy while fixing some
aspects of its structure. Another technique, also based on simulated
annealing, could start by generating a food web randomly with fixed
numbers of species and interactions and calculating its joint degree
distribution. Pairs of interactions could be swapped sequentially until
we minimize the divergence between the calculated joint degree
distribution and the one of maximum entropy obtained analytically. In
that case, this is the entropy of the joint degree distribution that
would be maximized, not the one of the network's topology. To a certain
extent, this method would thus bridge the gap between the two approaches
presented in this article (i.e.~analytical and heuristic MaxEnt models).
More research is needed to compare the quality of different methods
generating adjacency matrices of food webs using MaxEnt.

Another method generating adjacency matrices are maximum entropy graph
models, which predict a probability distribution of networks under soft
or hard constraints (e.g., Park and Newman 2004; Cimini et al. 2019).
Under hard constraints, every network with a non-zero probability
exactly satisfies the constraints on its structure. This is in contrast
with soft constraints, which require that networks satisfy them on
average (i.e.~many networks with a non-zero probability do not have the
exact structure set by the constraints). Maximum entropy graph models
are helpful because they can provide probability distributions for many
network properties, by measuring the structure of all adjacency matrices
with a non-zero probability. However, we consider that our approach
based on simulated annealing is more flexible and more computationally
efficient. Indeed, many measures of food-web structure are hard to
translate into mathematical constraints. Moreover, because food webs are
directed networks with self-loops, it makes the mathematical derivation
of maximum entropy graph models difficult. We believe that identifying
heuristically what really constrains the topology of food webs is a
useful first step before attempting to derive the mathematical
formulation of a maximum entropy graph model adapted to food webs.

\hypertarget{applications}{%
\subsection{Applications}\label{applications}}
